---
title: "Simple document"
output: html_document ###also can get a word_document, pdf_document###
date: 0910
author: Meitong Zhou
---  
```{r, echo=FALSE, messgae=FALSE}
library(tidyverse)
```

I loaded necessary packages 'tidyverse'

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r eval=FALSE} 
####show the things that you don't want show but don't want to delate####
samp = rnorm(100)
length(samp)
``` 
# Section 1.5
**opt+cmd+i**


# Section 2
I can take the mean of the sample, too!
The mean is `r mean(samp)`.
```{r}
# Section 3
2+3
```
This is code for learning assessment at P8105. it createss'la_df'
```{r la_chunk, message=FALSE}

la_df=
  tibble(
    norm_samp=rnorm(n=500,mean=1),
    samp_g0=norm_samp>0,
    abs_v_samp=abs(norm_samp)
)
ggplot(la_df, aes(x = abs_v_samp)) + geom_histogram()
```

```{r learning_assessment_1}
library(tidyverse)

la_df = tibble(
  norm_samp = rnorm(500, mean = 1),
  norm_samp_pos = norm_samp > 0,
  abs_norm_samp = abs(norm_samp)
)

ggplot(la_df, aes(x = abs_norm_samp)) + geom_histogram()

median_samp = median(pull(la_df, norm_samp))
```


 don't want comment shows 
echo and eval and put it in the new chunks



Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

